```{r}
#| include: false

objs <- readRDS(here::here("outputs", "objects", "analysis_script_objects.rds"))
list2env(objs, envir = knitr::knit_global())

library(kableExtra)
library(tidyverse)

```

# Tables

## Table 1. Eligibility criteria for including and excluding references in the overview {#sec-table1}

```{r}
#| #label: tbl-table1
#| #tbl-cap: "Inclusion and Exclusion Criteria"
#| echo: false
#| message: false
#| warning: false



# Define PICO elements
population_include    <- "Primary and secondary students (K-12 in the U.S.)"
population_exclude    <- "Pre-K, college students"

intervention_include  <- "Universal prevention, selective prevention, or indicated prevention delivered to students"
intervention_exclude  <- "Screening-only, treatment, or chronic case management interventions not delievered directly to students"

comparators_include   <- "Any comparison group"
comparators_exclude   <- "No comparison group"

outcomes_include      <- "Suicide (completed or attempted), suicidal ideation, parasuicide"
outcomes_exclude      <- "None"

timing_include        <- "Timing of follow-up not limited"
timing_exclude        <- "None"

setting_include       <- "Primary and secondary schools (K-12 in the U.S.)"
setting_exclude       <- "Non-school setting (e.g., community-based intervention)"

publications_include  <- "Systematic reviews with meta-analysis, published in 1900 or later, written in English, peer-reviewed and grey literature"
publications_exclude  <- "Full report not available, no meta-analysis of at least one suicide outcome, published before 1990"

# Assemble into a data frame
criteria_df <- tibble(
  Criteria = c("Population",
               "Interventions",
               "Comparators",
               "Outcomes",
               "Timing",
               "Setting",
               "Design and Publication"),
  Include  = c(population_include,
               intervention_include,
               comparators_include,
               outcomes_include,
               timing_include,
               setting_include,
               publications_include),
  Exclude  = c(population_exclude,
               intervention_exclude,
               comparators_exclude,
               outcomes_exclude,
               timing_exclude, 
               setting_exclude,
               publications_exclude)
)

# Render as an HTML table
criteria_df %>%
  kable(
    format    = "html",
    align     = c("l","l","l"),
    escape    = TRUE
  ) %>%
  kable_styling(
    full_width = FALSE,
    position   = "center",
    bootstrap_options = c("striped", "hover", "condensed")
  )

```


## Table 2. Descriptive characteristics of included systematic reviews {#sec-table2}

```{r}
#| #label: tbl-table2
#| #tbl-cap: "Review Characteristics"
#| echo: false
#| message: false
#| warning: false

table1_formatted

```


## Table 3. Methodological Quality of Included Systematic Reviews according to AMSTAR-2 Assessments {#sec-table3}

```{r}
#| #label: tbl-table3
#| #tbl-cap: "Quality Assessment"
#| echo: false
#| message: false
#| warning: false

t2_formatted

```

## Table 4. Risk of Bias in Included Systematic Reviews according to ROBIS Assessments {#sec-table4}

```{r}
#| #label: tbl-table4
#| #tbl-cap: "Risk of Bias Assessment"
#| echo: false
#| message: false
#| warning: false

t3_formatted

```

## Table 5. Overall meta-analytic estimates {#sec-table5}

```{r}

#| echo: false
#| message: false
#| warning: false

t5_formatted

```

## Table 6. Meta-analytic estimates by intervention type, contrasts, or non-primary outcomes {#sec-table6}

```{r}

#| echo: false
#| message: false
#| warning: false

t6_formatted

```




