
```{r}
#| include: false

library(ccaR)

objs <- readRDS(here::here("outputs", "objects", "analysis_script_objects.rds"))
list2env(objs, envir = knitr::knit_global())

```

# Appendices

## Appendix 1. List of Excluded Reviews {#sec-appendix1}

```{r}
#| #label: tbl-a1
#| #tbl-cap: "Excluded Reviews"
#| echo: false
#| message: false
#| warning: false

a1_formatted

```


## Appendix 2. List of Reviews Awaiting Classification {#sec-appendix2}

```{r}
#| #label: tbl-a2
#| #tbl-cap: "Reviews Awaiting Classification"
#| echo: false
#| message: false
#| warning: false

a3_formatted

```


## Appendix 3. Descriptive Characteristics for Included Systematic Reviews {#sec-appendix3}

```{r}
#| #label: tbl-a3
#| #tbl-cap: "Review Information"
#| echo: false
#| message: false
#| warning: false

# Print in document
htmltools::browsable(htmltools::HTML(html_code))

```

## Appendix 4. Overlap of Outcome-Specific Citation Matrices Across Systematic Reviews {#sec-appendix4}

### Suicidal Ideation Outcomes

```{r}
#| #label: fig-a4-1
#| #fig-cap: "Overlap of Suicidal Ideation Outcome Studies Across Reviews"
#| echo: false
#| message: false
#| warning: false
#| fig-width: 7
#| fig-height: 6
#| dpi: 300
#| out-width: "100%"

f4 <- cca_heatmap(ideation_cca_all, decimal_digits = 0, fontsize = 8, fontsize_diag = 5)


f4 +
  ggplot2::theme(
    plot.caption = ggplot2::element_text(size = 11, margin = ggplot2::margin(30,0,0,0)),
    legend.title = ggplot2::element_text(size = 16, face = "bold", vjust = 4),
    legend.text = ggplot2::element_text(size = 14),
    legend.key.size = ggplot2::unit(1.0, "cm"),
    legend.title.align = 0.5,
    legend.text.align = 0.5,
    axis.text.x = ggplot2::element_text(size = 18),
    axis.text.y = ggplot2::element_text(size = 18),
    axis.title = ggplot2::element_blank(),
    axis.ticks = ggplot2::element_blank(),
    axis.line = ggplot2::element_blank(),
    panel.border = ggplot2::element_blank(),
    panel.grid.major.x = ggplot2::element_line(colour = "grey80", linetype = "dashed")
  )

```

```{r}
#| #label: fig-a4-2
#| #fig-cap: "Overlap of Suicidal Ideation Outcome Studies Across Reviews (Current Review Eligible Studies)"
#| echo: false
#| message: false
#| warning: false
#| fig-width: 7
#| fig-height: 6
#| dpi: 300
#| out-width: "100%"

f5 <- cca_heatmap(ideation_cca_elig, decimal_digits = 0, fontsize = 8, fontsize_diag = 5)


f5 +
  ggplot2::theme(
    plot.caption = ggplot2::element_text(size = 11, margin = ggplot2::margin(30,0,0,0)),
    legend.title = ggplot2::element_text(size = 16, face = "bold", vjust = 4),
    legend.text = ggplot2::element_text(size = 14),
    legend.key.size = ggplot2::unit(1.0, "cm"),
    legend.title.align = 0.5,
    legend.text.align = 0.5,
    axis.text.x = ggplot2::element_text(size = 18),
    axis.text.y = ggplot2::element_text(size = 18),
    axis.title = ggplot2::element_blank(),
    axis.ticks = ggplot2::element_blank(),
    axis.line = ggplot2::element_blank(),
    panel.border = ggplot2::element_blank(),
    panel.grid.major.x = ggplot2::element_line(colour = "grey80", linetype = "dashed")
  )

```

### Suicide Attempt Outcomes

```{r}
#| #label: fig-a4-3
#| #fig-cap: "Overlap of Suicide Attempt Outcome Studies Across Reviews"
#| echo: false
#| message: false
#| warning: false
#| fig-width: 8
#| fig-height: 6
#| dpi: 300
#| out-width: "100%"

f6 <- cca_heatmap(attempts_cca_all, decimal_digits = 0, fontsize = 7, fontsize_diag = 5)

f6 +
  ggplot2::theme(
    plot.caption = ggplot2::element_text(size = 11, margin = ggplot2::margin(30,0,0,0)),
    legend.title = ggplot2::element_text(size = 16, face = "bold", vjust = 4),
    legend.text = ggplot2::element_text(size = 14),
    legend.key.size = ggplot2::unit(1.0, "cm"),
    legend.title.align = 0.5,
    legend.text.align = 0.5,
    axis.text.x = ggplot2::element_text(size = 16),
    axis.text.y = ggplot2::element_text(size = 16),
    axis.title = ggplot2::element_blank(),
    axis.ticks = ggplot2::element_blank(),
    axis.line = ggplot2::element_blank(),
    panel.border = ggplot2::element_blank(),
    panel.grid.major.x = ggplot2::element_line(colour = "grey80", linetype = "dashed")
  )

```

```{r}
#| #label: fig-a4-4
#| #fig-cap: "Overlap of Suicide Attempt Outcome Studies Across Reviews (Current Review Eligible Studies)"
#| echo: false
#| message: false
#| warning: false
#| fig-width: 8
#| fig-height: 6
#| dpi: 300
#| out-width: "100%"

f7 <- cca_heatmap(attempts_cca_elig, decimal_digits = 0, fontsize = 7, fontsize_diag = 5)

f7 +
  ggplot2::theme(
    plot.caption = ggplot2::element_text(size = 11, margin = ggplot2::margin(30,0,0,0)),
    legend.title = ggplot2::element_text(size = 16, face = "bold", vjust = 4),
    legend.text = ggplot2::element_text(size = 14),
    legend.key.size = ggplot2::unit(1.0, "cm"),
    legend.title.align = 0.5,
    legend.text.align = 0.5,
    axis.text.x = ggplot2::element_text(size = 16),
    axis.text.y = ggplot2::element_text(size = 16),
    axis.title = ggplot2::element_blank(),
    axis.ticks = ggplot2::element_blank(),
    axis.line = ggplot2::element_blank(),
    panel.border = ggplot2::element_blank(),
    panel.grid.major.x = ggplot2::element_line(colour = "grey80", linetype = "dashed")
  )

```

### Suicide-Related Competencies Outcomes

```{r}
#| #label: fig-a4-5
#| #fig-cap: "Overlap of Suicide-Related Competencies Outcome Studies Across Reviews"
#| echo: false
#| message: false
#| warning: false
#| fig-width: 7
#| fig-height: 6
#| dpi: 300
#| out-width: "100%"

f8 <- cca_heatmap(competencies_cca_all, decimal_digits = 0, fontsize = 8, fontsize_diag = 5)


f8 +
  ggplot2::theme(
    plot.caption = ggplot2::element_text(size = 11, margin = ggplot2::margin(30,0,0,0)),
    legend.title = ggplot2::element_text(size = 16, face = "bold", vjust = 4),
    legend.text = ggplot2::element_text(size = 14),
    legend.key.size = ggplot2::unit(1.0, "cm"),
    legend.title.align = 0.5,
    legend.text.align = 0.5,
    axis.text.x = ggplot2::element_text(size = 18),
    axis.text.y = ggplot2::element_text(size = 18),
    axis.title = ggplot2::element_blank(),
    axis.ticks = ggplot2::element_blank(),
    axis.line = ggplot2::element_blank(),
    panel.border = ggplot2::element_blank(),
    panel.grid.major.x = ggplot2::element_line(colour = "grey80", linetype = "dashed")
  )

```

```{r}
#| #label: fig-a4-6
#| #fig-cap: "Overlap of Suicide-Related Competencies Outcome Studies Across Reviews (Current Review Eligible Studies)"
#| echo: false
#| message: false
#| warning: false
#| fig-width: 7
#| fig-height: 6
#| dpi: 300
#| out-width: "100%"

f9 <- cca_heatmap(competencies_cca_elig, decimal_digits = 0, fontsize = 8, fontsize_diag = 5)


f9 +

  ggplot2::theme(
    plot.caption = ggplot2::element_text(size = 11, margin = ggplot2::margin(30,0,0,0)),
    legend.title = ggplot2::element_text(size = 16, face = "bold", vjust = 4),
    legend.text = ggplot2::element_text(size = 14),
    legend.key.size = ggplot2::unit(1.0, "cm"),
    legend.title.align = 0.5,
    legend.text.align = 0.5,
    axis.text.x = ggplot2::element_text(size = 18),
    axis.text.y = ggplot2::element_text(size = 18),
    axis.title = ggplot2::element_blank(),
    axis.ticks = ggplot2::element_blank(),
    axis.line = ggplot2::element_blank(),
    panel.border = ggplot2::element_blank(),
    panel.grid.major.x = ggplot2::element_line(colour = "grey80", linetype = "dashed")
  )

```
