---
title: "Suicide Prevention - Overview of Reviews - Descriptive Results"
author: "Shaina Trevino"
date: "2026-03-16"
output: html_document
---

```{r renv-setup}
## If renv environment does not load automatically, uncomment and run the below code:

# if (!require("renv)) install.packages("renv")
# renv::restore()

```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = FALSE)


library(rio)
library(here)
library(readxl)
library(janitor)
library(tidyverse)
library(openxlsx)
library(lubridate)
library(gt)
library(webshot2)
library(ccaR)
library(glue)

## If library didn't work, try un-commenting and running the below code:

# if (!require("pacman")) install.packages("pacman") #installs and loads pacman package
# 
# pacman::p_load(devtools, rio, here, readxl, janitor, tidyverse, openxlsx, lubridate, gt, webshot2, glue) #install and load required packages
# pacman::p_load_gh("thdiakon/ccaR", "mcguinlu/robvis") #from github



```

```{r import}
# Eligibility (with linked refs; datarama report)
spo_eligibility_raw <- import(here("data", "SPO_screening_eligibility.xlsx")) %>% 
  janitor::clean_names()
# Check unique IDs
length(unique(spo_eligibility_raw$refid)) == nrow(spo_eligibility_raw)

# Import Quarantine Duplicates (Download from DistillerSR Quarantine)
spo_duplicates <- import(here("data", "SPO_duplicate_refs.csv")) %>% 
  janitor::clean_names()

# Import Review Level Data
spo_review_level <- import(here("data", "SPO_review_level.xlsx")) %>% 
  janitor::clean_names()


# Import citation matrix
elig_path <- here("data", "Suicide_citation_matrix_reconciled.xlsx")

citation_matrix <- read_excel(elig_path, sheet = "Citation Matrix", col_names = FALSE)


```

```{r tidy}
# eligibility
colnames(citation_matrix) <- citation_matrix[1,]
td_cm <- citation_matrix %>% 
  slice(-1)

spo_eligibility <- spo_eligibility_raw %>% 
  mutate(
    eligibility_exclude_reason = if_else(
      !is.na(eligibility_notes) &
        str_detect(eligibility_notes, fixed("; Study")) &
        eligibility_exclude_reason == "Unclear (provide reason in comments)",
      "Ineligible study design (not a systematic review or primary study)",
      eligibility_exclude_reason
    )
  )


#review level
review_td <- spo_review_level %>% 
  select(-starts_with("amstar"), -starts_with("robis")) %>% 
  mutate(review_publication_year = as.numeric(review_publication_year))

amstar_rating_td <- spo_review_level %>% 
  select(refid, review_author_year, starts_with("amstar")) %>% 
  select(refid, review_author_year, ends_with("rating"))

robis_rating_td <- spo_review_level %>% 
  select(refid, review_author_year, starts_with("robis")) %>% 
  select(refid, review_author_year, ends_with("decision"), robis_overall_a, robis_overall_b, robis_overall_c, 
         robis_overall_rating)

```


```{r functions}
#Write functions for formatting inline code
format_thousands <- function(x) {
  big_num <- format(x, big.mark = ",")
  return(big_num)
}

format_percent <- function(x, digits, force_decimal = FALSE) {
  if (force_decimal) {
    percentage <- paste0(format(round(x, digits), nsmall = digits), "%")
  } else {
    percentage <- paste0(round(x, digits), "%")
  }
  return(percentage)
}
```



# Results

```{r exclude_reasons}
summary(as.factor(spo_eligibility$eligibility_exclude_reason))

overview_counts <- list(
  records_identified = nrow(spo_eligibility) + nrow(spo_duplicates),
  records_screened = nrow(spo_eligibility),
  records_kept = sum(spo_eligibility$screening_decision == "Keep", na.rm = TRUE),
  reports_not_retrieved = sum(spo_eligibility$pdf_retrieved == "No", na.rm = TRUE),
  reports_assessed = sum(spo_eligibility$screening_decision == "Keep", na.rm = TRUE) - 
    sum(spo_eligibility$pdf_retrieved == "No", na.rm = TRUE),
  reviews_included = nrow(spo_review_level),
  reports_included = sum(
    spo_eligibility$eligibility_decision == "Eligible" &
      spo_eligibility$eligibility_reference_type == "Review",
    na.rm = TRUE
  )
)

# Percentages
overview_counts$prop_kept <- overview_counts$records_kept / overview_counts$records_screened * 100
overview_counts$prop_ref_assessed <- overview_counts$reports_assessed / overview_counts$records_screened * 100
overview_counts$prop_reviews_assessed <- overview_counts$reviews_included / overview_counts$reports_assessed * 100
overview_counts$prop_reviews_identified <- overview_counts$reviews_included / overview_counts$records_identified * 100

```

Our search yielded `r format_thousands(overview_counts$records_identified)` citations (see *Figure 1*). 
After removing duplicates, we screened `r format_thousands(overview_counts$records_screened)` records and retained `r format_thousands(overview_counts$reports_assessed)` records (`r format_percent(overview_counts$prop_ref_assessed, 1)`) for full-text eligibility assessment. Of the `r format_thousands(overview_counts$reports_assessed)` full-texts assessed, we identified `r format_thousands(overview_counts$reviews_included)` eligible systematic reviews with information reported across `r format_thousands(overview_counts$reports_included)` records (`r format_percent(overview_counts$prop_reviews_assessed, 1)` of full-texts assessed for eligibility; `r format_percent(overview_counts$prop_reviews_identified, 1)` of all citations identified in our search). *Appendix 3* contains detailed information on the `r format_thousands(overview_counts$reviews_included)` included systematic reviews.

## Characteristics of Included Systematic Reviews

```{r review-char}
#Calculate most commonly searched databases
#change string to lowercase and create flag if each database was searched
rev_df <- review_td %>% 
  mutate(review_databases_searched = str_to_lower(review_databases_searched),
         pubmed = str_detect(review_databases_searched, "pubmed"),
         psycinfo = str_detect(review_databases_searched, "psycinfo"),
         medline = str_detect(review_databases_searched, "medline|ovid"),
         eric = str_detect(review_databases_searched, "eric|education resources information center"),
         ebsco = str_detect(review_databases_searched, "ebsco"),
         proquest_dt = str_detect(review_databases_searched, "dissertation and theses|dissertation results on proquest"),
         psycarticles = str_detect(review_databases_searched, "psycarticles"),
         psycextra = str_detect(review_databases_searched, "psycextra|psychextra"),
         cochrance_central = str_detect(review_databases_searched, "cochrane central"),
         cochrane_library = str_detect(review_databases_searched, "cochrane library"),
         wos = str_detect(review_databases_searched, "web of science"),
         academic_ap = str_detect(review_databases_searched, "academic search premier"),
         pbs_collection = str_detect(review_databases_searched, "psychology and behavioral sciences collection|psychology and behavioralsciences"),
         cinahl = str_detect(review_databases_searched, "cinahl"),
         embase = str_detect(review_databases_searched, "embase"),
         science_cit_index = str_detect(review_databases_searched, "science citation index"),
         sci_direct = str_detect(review_databases_searched, "science direct|sciencedirect"),
         scopus = str_detect(review_databases_searched, "scopus"),
         gscholar = str_detect(review_databases_searched, "google scholar|googlescholar"),
         british_ni = str_detect(review_databases_searched, "british nursing index"),
         britich_ei = str_detect(review_databases_searched, "british education index"),
         assia = str_detect(review_databases_searched, "assia"),
         diss_abs = str_detect(review_databases_searched, "dissertation abstracts"),
         socio_abs = str_detect(review_databases_searched, "sociological abstracts"),
         won = str_detect(review_databases_searched, "web of knowledge"),
         ctg = str_detect(review_databases_searched, "clinicaltrials.gov"),
         prosp = str_detect(review_databases_searched, "prospero"),
         optn  = str_detect(review_databases_searched, "opentrials.net"), #Added for suicide
         edrc = str_detect(review_databases_searched, "education research complete"), #Added for suicide
         edsrc = str_detect(review_databases_searched, "education source"), #Added for suicide
         epist = str_detect(review_databases_searched, "epistemonikos"))

#create long dataframe
review_databases <- rev_df %>% 
  select(refid, pubmed:epist) %>% 
  pivot_longer(cols = pubmed:epist) %>% 
  mutate(value = as.character(value))

#calculate most common databases searched and 
#remove cases where reviews said both pubmed and medline but only searched one
mode_databases <- review_databases %>% 
  group_by(name) %>% 
  summarize(num_db = sum(value == "TRUE"),
            percent = sum(value == "TRUE") / nrow(review_td) * 100) %>% 
  arrange(desc(num_db))

#Year of last database search
#extract review year from search data
review_df <- review_td %>% 
  mutate(db_search_year = as.numeric(str_extract(review_search_date, "[0-9]{4}")))

#Transparency
#number of reviews with flow diagrams
num_prisma <- sum(review_df$review_flow_diagram == "Yes", na.rm = TRUE) 

#number of reviews with registration number
num_reg <- sum(review_df$review_registration_number != "-999") 

#number of reviews with availability statements
num_avail <- sum(review_df$review_availability_statement != "-999")


```


Overall, these `r nrow(review_td)` reviews were published between `r min(review_td$review_publication_year)` and `r max(review_td$review_publication_year)`, with a median publication year of `r median(review_td$review_publication_year)` (see *Table 1*). These reviews most commonly searched  *APA PsycInfo* (`r mode_databases$num_db[1]` reviews; `r format_percent(mode_databases$percent[1], 1)`), *Cochrane Central Register of Controlled Trials* (`r mode_databases$num_db[2]` reviews; `r format_percent(mode_databases$percent[2], 1)`), *MEDLINE* (`r mode_databases$num_db[3]` reviews; `r format_percent(mode_databases$percent[3], 1)`), and *ERIC* (`r mode_databases$num_db[4]` reviews; `r format_percent(mode_databases$percent[4], 1)`) to identify primary studies. The year that each review last conducted their literature search ranged from `r min(review_df$db_search_year, na.rm = TRUE)` to `r max(review_df$db_search_year, na.rm = TRUE)`, with a median of `r ceiling(median(review_df$db_search_year, na.rm = TRUE))`. Regarding research transparency, `r num_prisma` reviews (`r format_percent(num_prisma / nrow(review_df) * 100, 1)`) included a flow diagram of information through the different phases of a systematic review (Page et al., 2021), `r num_reg` reviews (`r format_percent(num_reg / nrow(review_df) * 100, 1)`) reported a registration number for their review (Booth et al., 2012), and `r num_avail` reviews (`r format_percent(num_avail / nrow(review_df) *100, 1)`) provided statements about the data and code underlying the review (Page et al., 2022). 

### Methodological Quality and Risk of Bias of Included Systematic Reviews

```{r rob-inline}
#number/% of high confidence
amstar_high <- sum(amstar_rating_td$amstar_overall_rating == "HIGH") 
amstar_high_per <- amstar_high  / nrow(amstar_rating_td) * 100 

#number/% of moderate confidence
amstar_mod <- sum(amstar_rating_td$amstar_overall_rating == "MODERATE")
amstar_mod_per <- amstar_mod  / nrow(amstar_rating_td) * 100 

#number/% of low confidence
amstar_low <- sum(amstar_rating_td$amstar_overall_rating == "LOW")
amstar_low_per <- amstar_low  / nrow(amstar_rating_td) * 100 

#number/% of critically low confidence
amstar_clow <- sum(amstar_rating_td$amstar_overall_rating == "CRITICALLY LOW")
amstar_clow_per <- amstar_clow  / nrow(amstar_rating_td) * 100 

#Calculate most common critical weaknesses in AMSTAR ratings among reviews
#filter for critical domains
amstar_crit <- amstar_rating_td %>% 
  select(refid, amstar_2_rating, amstar_4_rating, amstar_7_rating, amstar_9rct_rating, amstar_9nrsi_rating,
         amstar_11rct_rating, amstar_11rct_rating, amstar_13_rating, amstar_15_rating) %>% 
  pivot_longer(cols = -refid)

#calculate frequency for "No"s per critical domains
amstar_crit_mode <- amstar_crit %>% 
  group_by(name) %>% 
  summarize(n = sum(value == "No"),
            percent = sum(value == "No") / nrow(amstar_rating_td) * 100) %>% 
  arrange(desc(n))

#Calculate most common non-critical weaknesses in AMSTAR ratings among reviews
#filter for non-critical domains
amstar_noncrit <- amstar_rating_td %>% 
  select(refid, amstar_1_rating, amstar_3_rating, amstar_5_rating, amstar_6_rating, amstar_8_rating, 
         amstar_10_rating, amstar_12_rating, amstar_14_rating, amstar_16_rating) %>% 
  pivot_longer(cols = -refid)

#calculate frequency for "No"s per non-critical domains
amstar_noncrit_mode <- amstar_noncrit %>% 
  group_by(name) %>% 
  summarize(n = sum(value == "No"),
            percent = sum(value == "No") / nrow(amstar_rating_td) * 100) %>% 
  arrange(desc(n))

#ROBIS results
#number/% of low risk
robis_low <- sum(robis_rating_td$robis_overall_rating == "LOW")
robis_low_per <- robis_low  / nrow(robis_rating_td) * 100 

#number/% of unclear risk
robis_unclear <- sum(robis_rating_td$robis_overall_rating == "UNCLEAR") 
robis_unclear_per <- robis_unclear  / nrow(robis_rating_td) * 100 

#number/% of high risk
robis_high <- sum(robis_rating_td$robis_overall_rating == "HIGH") 
robis_high_per <- robis_high  / nrow(robis_rating_td) * 100 

#select ratings, transform to long format, calculate percent with high risk
robis_concerns <- robis_rating_td %>% 
  select(refid, ends_with("decision"), robis_overall_a, 
         robis_overall_b, robis_overall_c) %>% 
  pivot_longer(cols = 2:8) %>% 
  group_by(name) %>% 
  summarize(n_decision = sum(value == "HIGH"),
            per_decision = sum(value == "HIGH") / nrow(robis_rating_td) * 100,
            n_overall = sum(value == "No"),
            per_overall = sum(value == "No") / nrow(robis_rating_td) * 100) %>% 
  arrange(desc(n_decision))


```


AMSTAR-2 assessments (see *Table 2*) yielded methodological quality ratings of low for `r amstar_low` reviews (`r format_percent(amstar_low_per, 1)`) and critically low for `r amstar_clow` reviews (`r format_percent(amstar_clow_per, 1)`). The most common critical weaknesses in methodological quality were *not providing justification for excluding individual studies* (`r amstar_crit_mode$n[1]` reviews; `r format_percent(amstar_crit_mode$percent[1], 1)`), *not considering risk of bias when interpreting the results of the review* (`r amstar_crit_mode$n[2]` reviews; `r format_percent(amstar_crit_mode$percent[2], 1)`), and *not having a protocol registered before commencement of the review* (`r amstar_crit_mode$n[3]` reviews; `r format_percent(amstar_crit_mode$percent[3], 1)`). 

The most common non-critical weaknesses in methodological quality were *not reporting funding sources for included studies* (`r amstar_noncrit_mode$n[1]` reviews; `r format_percent(amstar_noncrit_mode$percent[1], 1)`), *not assessing the impact of risk of bias in individual studies on evidence synthesis results* (`r amstar_noncrit_mode$n[2]` reviews; `r format_percent(amstar_noncrit_mode$percent[2], 1)`), and *not explaining the selection criteria used to identify included study designs* (`r amstar_noncrit_mode$n[3]` reviews; `r format_percent(amstar_noncrit_mode$percent[3], 1)`). 

ROBIS assessments (see *Table 3*) yielded ratings of low risk of bias for `r robis_low` reviews (`r format_percent(robis_low_per, 1)`, unclear risk of bias for `r robis_unclear` review `r format_percent(robis_unclear_per, 1)`), and high risk of bias for `r robis_high` reviews (`r format_percent(robis_high_per, 1)`). Concerns about risk of bias were most commonly related to *study eligibility criteria* (`r robis_concerns$n_decision[1]` reviews; `r format_percent(robis_concerns$per_decision[1], 1)`), *identification and selection of studies* (`r robis_concerns$n_decision[2]` reviews; `r format_percent(robis_concerns$per_decision[2], 1)`), and *synthesis and findings* (`r robis_concerns$n_decision[3]` reviews; `r format_percent(robis_concerns$per_decision[3], 1)`).


### Overlap of Primary Studies Across Systematic Reviews

```{r overlap}
#number of included primary studies
#num_elig_stud <- length(inc_ps)

#using citation matrix without headers, transpose data 
cmt <- as.data.frame(t(citation_matrix))


#remove first row of column names and second row with current study inclusions
#create new variable to calculate number of studies in each review
df_overlap <- cmt %>% 
  slice(-1) %>% 
  mutate(num_stud = rowSums(. == "Yes")) 

#range and median of number of studies in each review
range(df_overlap$num_stud) 
median(df_overlap$num_stud) 

#Number and percentage of primary studies included in more than one review
#create flag for if study is in more than one review
cm_overlap <- td_cm %>% 
  #select(-`Current Review`, -refid) %>% 
  mutate(morethanone = ifelse(rowSums(. == "Yes") > 1, "yes", "no"))

#number and % included in more than one review
num_inc_overlap <- sum(cm_overlap$morethanone == "yes")
num_inc_overlap_per <- sum(cm_overlap$morethanone == "yes") / nrow(cm_overlap) * 100

# #Number and percentage of eligible primary studies included in more than one review
# #filter for eligible primary studies
# elig_cm <- ps_cm %>%
#   filter(refid %in% inc_ps) %>% 
#   select(-`Current Review`, -refid)
# 
# #create flag if eligible study is included in more than one review
# elig_overlap <- elig_cm %>%
#   mutate(morethanone = ifelse(rowSums(. == "1 - Yes") >1, "yes", "no"))
# 
# #number and % of eligible studies included in more than one review
# num_elig_overlap <- sum(elig_overlap$morethanone == "yes")
# num_elig_overlap_per <- ifelse(num_elig_overlap == 0, 0, num_elig_overlap / nrow(elig_overlap) * 100)

#Overall CCA percentage for all primary studies included across reviews
#create dataframe for ccaR input (1 = included; 0 = excluded)
ccar_input <- td_cm %>% 
  #select(-`Current Review`, -refid) %>% 
  mutate_at(vars(-study), ~ifelse(. == "Yes", 1, 0))  

#calculate overall CCA
cca_included <- cca(ccar_input) 
cca_included

# #Overall CCA percentage for primary studies meeting our eligibility criteria
# ccar_input_elig <- ps_cm %>% 
#   filter(refid %in% inc_ps) %>% 
#   select(-`Current Review`, -refid) %>% 
#   mutate_at(vars(-study), ~ifelse(. == "1 - Yes", 1, 0)) 
# 
# #calculate overall CCA
# cca_eligible <- cca(ccar_input_elig)
# cca_eligible


#REMOVED
 # Of the `r num_elig_stud` primary studies meeting our eligibility criteria, `r num_elig_overlap` studies (`r format_percent(num_elig_overlap_per, 1)`) were included in more than one review (see *Figure 3*).
#lower than the overall CCA percentage for primary studies meeting our eligibility criteria (`r format_percent(cca_eligible$CCA_Percentage, 1)`)
```


The number of primary studies included in each review ranged from `r min(df_overlap$num_stud)` to `r max(df_overlap$num_stud)`, with a median of `r round(median(df_overlap$num_stud))`. Of the `r nrow(td_cm)` primary studies included across all reviews, `r num_inc_overlap` studies (`r format_percent(num_inc_overlap_per, 1)`) were included in more than one review (see *Figure 2*). The overall CCA percentage for all primary studies included across reviews was `r format_percent(cca_included$CCA_Percentage, 1)`, indicating *high* overlap in primary studies across reviews.


# Figures, Tables, Appendices

### Figure 1. PRISMA

```{r PRISMA}



# Function for PRISMA for Overviews - from make_prisma_diagrams.R (HEDCO R project)
make_prisma_overview_plot <- function(elig_df, dupe_df, review_df) {
  
  # Create objects needed from variables
  number_of_duplicates <- nrow(dupe_df)
  number_search_results <- nrow(elig_df) + number_of_duplicates
  number_dropped <- sum(elig_df$screening_decision == "Drop")
  number_kept <- sum(elig_df$screening_decision == "Keep")
  number_not_retrieved <- sum(elig_df$pdf_retrieved == "No", na.rm = TRUE)
  number_ineligible <- sum(elig_df$eligibility_decision == "Not Eligible" | elig_df$eligibility_reference_type == "Study", na.rm = TRUE)
  number_eligible <- nrow(review_df)
  number_eligible_reports <- sum(elig_df$eligibility_decision == "Eligible" & elig_df$eligibility_reference_type == "Review", na.rm = TRUE)
  
  # Calculate exclusion counts
  exclusion_reasons_summary <- elig_df %>% 
    mutate(reason = dplyr::case_when(
      eligibility_reference_type == "Study" ~ "Ineligible study design",
      TRUE ~ as.character(eligibility_exclude_reason))) %>% 
    filter(!is.na(reason)) %>% 
    count(reason, name = "n") %>% 
    arrange(desc(n))
  
  # Define PRISMA Counts
  records_identified <- number_search_results
  duplicates_removed <- number_of_duplicates
  records_screened <- records_identified - duplicates_removed
  records_excluded <- number_dropped
  reports_sought <- number_kept
  reports_not_retrieved <- number_not_retrieved
  reports_assessed <- reports_sought - reports_not_retrieved
  reports_excluded_total <- number_ineligible
  studies_included <- number_eligible
  reports_included <- number_eligible_reports
  
  
  # Expose as a named vector for easy glue’ing
  exclusion_counts <- setNames(
    exclusion_reasons_summary$n,
    exclusion_reasons_summary$reason
  )
  
  # Collapse into markdown bullets
  bullet_text <- glue_collapse(
    glue("- {names(exclusion_counts)}: {exclusion_counts}"),
    sep = "\n"
  )
  
  cat(bullet_text)
  
  
  # # Define Exclusion Reasons (Correctly Formatted with Line Breaks)
  # exclusion_reasons <- glue("
  # - Ineligible concept (not 4DSW): {159}
  # - Ineligible context (not K-12): {9}
  # - Ineligible context (not US): {16}
  # - Ineligible design (not empirical research): {180}
  # - Ineligible publication (not English): {3}
  # ")
  
  
  ## PLOT -------
  
  # Define box content: x, y = center positions; label = box text
  boxes <- tibble(
    x = c(3, 6.5, 3, 6.5, 3, 6.5, 3, 6.5, 3),
    y = c(9, 9, 7.5, 7.5, 6, 6, 4.5, 3.9, 3),
    height = c(rep(1, 7), 2.8, 1),
    width  = c(rep(2.6, 7), 3.5, 2.6),
    label = c(
      glue("Records identified\n(n = {formatC(records_identified, format = 'd', big.mark = ',')})"),
      glue("Duplicates removed\n(n = {formatC(duplicates_removed, format = 'd', big.mark = ',')})"),
      glue("Records screened\n(n = {formatC(records_screened, format = 'd', big.mark = ',')})"),
      glue("Records excluded\n(n = {formatC(records_excluded, format = 'd', big.mark = ',')})"),
      glue("Reports sought\n(n = {formatC(reports_sought, format = 'd', big.mark = ',')})"),
      glue("Not retrieved\n(n = {formatC(reports_not_retrieved, format = 'd', big.mark = ',')})"),
      glue("Assessed for eligibility\n(n = {formatC(reports_assessed, format = 'd', big.mark = ',')})"),
      NA_character_,
      glue("Studies included\n(n = {formatC(studies_included, format = 'd', big.mark = ',')})\nReports = {formatC(reports_included, format = 'd', big.mark = ',')}")
    ),
    label_top = NA_character_,
    label_bullets = NA_character_
  )
  
  # Centered top line for “Reports excluded”
  boxes$label_top[8] <- glue(
    "Reports excluded\n(n = {formatC(reports_excluded_total, format = 'd', big.mark = ',')})\n"
  )
  
  
  # Dynamically inject the bullets for row 8
  boxes$label_bullets[8] <- bullet_text
  
  
  # Define arrow segments (from_x, from_y, to_x, to_y)
  arrows <- tribble(
    ~x,  ~y,   ~xend, ~yend,
    3,   8.5,    3,     8,   # Records identified → Records screened
    4.3,   9,    5.2,     9,     # Records identified → Duplicates removed
    3,   7,  3,     6.5,     # Records screened → Reports sought
    4.3,   7.5,  5.2,     7.5,   # Records screened → Records excluded
    3,   5.5,    3,     5,   # Reports sought → Assessed for eligibility
    4.3,   6,    5.2,     6,     # Reports sought → Not retrieved
    3,   4,  3,     3.5,     # Assessed → Included
    4.3,   4.5,  4.75,     4.5    # Assessed → Reports excluded
  )
  
  # Define section headers
  sections <- data.frame(
    label = c("Identification", "Screening", "Included"),
    x = c(1, 1, 1),
    y = c(9, 6, 3),
    height = c(1.6, 4.1, 1.5)
  )
  
  
  # Plot
  ggplot() +
    # Boxes
    geom_rect(data = boxes, aes(xmin = x - width/2, xmax = x + width/2,
                                ymin = y - height/2, ymax = y + height/2),
              fill = "white", color = "black") +
    
    # geom_text(data = boxes, aes(x = x, y = y, label = label),
    #           size = 3, lineheight = 1.1) +
    
    # Normal text
    geom_text(data = boxes, aes(x = x, y = y, label = label), size = 3.2, lineheight = 1.1) +
    
    # Centered top line for reports excluded
    geom_text(data = boxes[8, ], aes(x = x, y = y + 1.1, label = label_top),
              size = 3.2, hjust = 0.5, lineheight = 1.1) +
    
    # Left-aligned bullets
    geom_text(data = boxes[8, ], aes(x = x - 1.55, y = y - 0.25, label = label_bullets),
              size = 3, hjust = 0, lineheight = 1.1) +
    
    
    # Arrows
    geom_segment(data = arrows,
                 aes(x = x, y = y, xend = xend, yend = yend),
                 arrow = arrow(length = unit(0.15, "inches")),
                 lineend = "round") +
    
    # Section header background
    geom_rect(data = sections,
              aes(xmin = x - 0.25, xmax = x + 0.25,
                  ymin = y - height / 2, ymax = y + height / 2),
              fill = "lightblue", color = NA) +
    
    # Section header text
    geom_text(data = sections,
              aes(x = x, y = y, label = label),
              angle = 90, size = 4) +
    
    coord_equal() +
    theme_void()
  
}

# USE THE FUNCTION ON SUICIDE DATA 

# If needed, rename Exclusion reasons
spo_eligibility <- spo_eligibility %>%
  mutate(
    eligibility_exclude_reason = eligibility_exclude_reason %>%
      stringr::str_remove_all("\\s*\\([^)]*\\)") %>%  #remove " (anything)"
      stringr::str_trim()                             #remove leading/trailing spaces
  )

spo_overview_prisma <- make_prisma_overview_plot(elig_df = spo_eligibility, dupe_df = spo_duplicates, review_df = spo_review_level)

spo_overview_prisma

#ggsave(filename = "outputs/figures/SPO_PRISMA.png", spo_overview_prisma)


```


### Figure 2. Overlap of included studies across systematic reviews

Create CCA heatmap of overlap of included studies across reviews:

```{r ccaR-f2}
asterisk_studies <- td_cm %>%
  filter(str_detect(study, "\\*$")) %>%
  pull(study) %>%
  str_remove("\\*$")

# Helper function to buid caption text
asterisk_caption <- if(length(asterisk_studies) == 0){
  NULL
} else if(length(asterisk_studies) == 1){
  glue("Only meta-analyzed studies were reported for {asterisk_studies}.")
} else {
  study_text <- toString(asterisk_studies)
  study_text <- sub(", ([^,]+)$", ", and \\1", study_text)
  glue("Only meta-analyzed studies were reported for {study_text}")
}

# Identify review columns with trailing asterisks
starred_reviews <- names(td_cm) %>%
  .[. != "study"] %>%
  .[str_detect(., "\\*$")] %>%
  str_remove("\\*$")

# Create sentence for caption
star_note <- if(length(starred_reviews) == 0){
  NULL
} else if(length(starred_reviews) == 1){
  glue("Only meta-analyzed studies were reported for {starred_reviews}")
} else if(length(starred_reviews) == 2){
  glue("Only meta-analyzed studies were reported for {starred_reviews[1]} and {starred_reviews[2]}")
} else {
  glue(
    "Only meta-analyzed studies were reported for {paste(starred_reviews[-length(starred_reviews)], collapse = ', ')}, and {starred_reviews[length(starred_reviews)]}"
  )
}

# Remove trailing asterisks from review column names
td_cm_clean <- td_cm
names(td_cm_clean) <- names(td_cm_clean) %>%
  str_replace("\\*$", "")

#format citation matrix including our review
cca_inc <- td_cm_clean %>% 
  #select(-refid) %>% 
  mutate_at(vars(-study), ~ifelse(. == "Yes", 1, 0)) 

#Create heatmap first
f2 <- cca_heatmap(cca_inc, decimal_digits = 0, fontsize = 12, fontsize_diag = 8)

#Grab existing caption from cca_heatmap and append note
existing_caption <- f2$labels$caption
combined_caption <- paste(
  c(existing_caption, star_note),
  collapse = "\n"
)

# #create pairwise heatmap with CCA(%), including our review
# f2 <- cca_heatmap(cca_inc, decimal_digits = 0, fontsize = 12, fontsize_diag = 8) +
#   ggplot2::labs(caption = asterisk_caption) +
#   ggplot2::theme(
#       plot.caption = ggplot2::element_text(size = 20, margin=ggplot2::margin(30,0,0,0)),
#       legend.title = ggplot2::element_text(size = 20, face = "bold", vjust=4),
#       legend.text  = ggplot2::element_text(size = 20),
#       legend.key.size = ggplot2::unit(1.0, "cm"),
#       legend.title.align = 0.5,
#       legend.text.align = 0.5,
#       axis.text.x=ggplot2::element_text(size = 26),
#       axis.text.y=ggplot2::element_text(size = 26),
#       axis.title=ggplot2::element_blank(),
#       axis.ticks=ggplot2::element_blank(),
#       axis.line=ggplot2::element_blank(),
#       panel.border=ggplot2::element_blank(),
#       panel.grid.major.x=ggplot2::element_line(colour = "grey80", linetype = "dashed"))

#Apply updated caption and theme
f2 <- f2 +
  ggplot2::labs(caption = combined_caption) +
  ggplot2::theme(
    plot.caption = ggplot2::element_text(size = 20, margin = ggplot2::margin(30,0,0,0)),
    legend.title = ggplot2::element_text(size = 20, face = "bold", vjust = 4),
    legend.text = ggplot2::element_text(size = 20),
    legend.key.size = ggplot2::unit(1.0, "cm"),
    legend.title.align = 0.5,
    legend.text.align = 0.5,
    axis.text.x = ggplot2::element_text(size = 26),
    axis.text.y = ggplot2::element_text(size = 26),
    axis.title = ggplot2::element_blank(),
    axis.ticks = ggplot2::element_blank(),
    axis.line = ggplot2::element_blank(),
    panel.border = ggplot2::element_blank(),
    panel.grid.major.x = ggplot2::element_line(colour = "grey80", linetype = "dashed")
  )

f2

```

Save figure 2 to `outputs/figures` project folder: 

```{r save-f2}
# #set image dimensions and file path to save
# png(here("outputs", "figures", "figure2_heatmap.png"), width = 1000, height = 1000)
# 
# #show plot
# f2
# 
# #save png of plot
# dev.off()
```

### Figure 3. Overlap of eligible studies across systematic reviews

Filter for studies that met our inclusion criteria and create CCA heatmap of our eligible studies across reviews: 

```{r ccaR-elig-f3}
# #format citation matrix of eligible studies, including our review
# cca_elig <- ps_cm %>% 
#   filter(refid %in% inc_ps_wlinked) %>% 
#   select(-refid) %>% 
#   mutate_at(vars(-study), ~ifelse(. == "1 - Yes", 1, 0))  %>% 
#   rename(` Current Review` = `Current Review`)
# 
# #create pairwise heatmap with CCA(%)
# f3 <- cca_heatmap(cca_elig, decimal_digits = 0, fontsize = 7.5, fontsize_diag = 4.5) +
#   ggplot2::theme(
#       plot.caption = ggplot2::element_text(size = 16, margin=ggplot2::margin(30,0,0,0)),
#       legend.title = ggplot2::element_text(size = 16, face = "bold", vjust=4),
#       legend.text = ggplot2::element_text(size = 16),
#       legend.key.size = ggplot2::unit(1.0, "cm"),
#       legend.title.align = 0.5,
#       legend.text.align = 0.5,
#       axis.text.x = ggplot2::element_text(size = 22),
#       axis.text.y = ggplot2::element_text(size = 22),
#       axis.title = ggplot2::element_blank(),
#       axis.ticks = ggplot2::element_blank(),
#       axis.line = ggplot2::element_blank(),
#       panel.border = ggplot2::element_blank(),
#       panel.grid.major.x = ggplot2::element_line(colour = "grey80", linetype = "dashed"))
# 
# print(f3)

```

Save figure 3 to `outputs/figures` project folder: 

```{r save-f3}
# #set image dimensions and file path to save
# png(here("outputs", "figures", "figure3_heatmap.png"), width = 1000, height = 1000)
# 
# #show plot
# f3
# 
# #save png of plot
# dev.off()
```


### Table 1. Descriptive characteristics per each included systematic review

```{r t1-reviewchar}
#select info we for table1
t1_info <- review_td %>% 
  select(refid, review_author_year, review_databases_searched, review_search_date)

#transform to long to calculate # of included/eligible studies per review
cm_long <- td_cm %>% 
  pivot_longer(cols = -study,
               names_to = "review_author_year") 

#count number of included studies per review
numinc_perreview <- cm_long %>% 
  group_by(review_author_year) %>% 
  summarize(n_included = sum(value == "Yes", na.rm = TRUE)) %>% 
  ungroup() %>% 
  mutate(review_author_year = str_remove(review_author_year, "\\*$")) 

# #create list of included study names for merging
# inc_ps_name <- td_cm %>% 
#   filter(refid %in% inc_ps_wlinked) %>% 
#   pull(study)
# 
# #count number of eligible studies per review
# numelig_perreview <- cm_long %>% 
#   filter(study %in% inc_ps_name) %>% 
#   group_by(review_author_year) %>% 
#   summarize(n_eligible = sum(value == "1 - Yes", na.rm = TRUE)) %>% 
#   ungroup()

#merge and format values
t1 <- left_join(t1_info, numinc_perreview) %>% 
  #left_join(numelig_perreview) %>% 
  mutate(search_date_format = ifelse(nchar(review_search_date) == 10, format(ymd(review_search_date), "%B %d, %Y"), review_search_date)) %>% 
  mutate(search_date_format = ifelse(nchar(review_search_date) == 7, format(ym(review_search_date), "%B %Y"), search_date_format)) %>% 
  mutate_all(~ replace(., . == -999, "Not Reported")) %>% 
  select(review_author_year, review_databases_searched, search_date_format, n_included) %>% #, n_eligible
  arrange(str_to_lower(review_author_year))

#create gt table and format
table1_formatted <- t1 %>% 
  gt() %>% 
  cols_align(columns = c("n_included"), align = "center") %>% #, "n_eligible"
  tab_style(style = cell_text(align = "left"), locations = cells_column_labels(columns = c("n_included"))) %>% #, "n_eligible"
  cols_width(review_author_year ~ px(125), review_databases_searched ~ px(275), search_date_format ~ px(150), starts_with("n") ~ px(75)) %>% 
  cols_label(review_author_year = "Review", 
            review_databases_searched = "Databases Searched",
            search_date_format = "Search Date",
            n_included = "Included Studies"#,
            #n_eligible = "Eligible Studies"
            ) %>% 
  tab_style(style = list(cell_borders(sides = "all", color = "black", weight = px(1))),
            locations = cells_body(columns = everything())) %>% 
  tab_style(style = list(cell_borders(sides = "all", color = "black", weight = px(1)),
                         cell_text(weight = "bold")),
            locations = cells_column_labels()) %>% 
  tab_options(column_labels.border.top.color = "black",
              column_labels.border.bottom.color = "black",
              table_body.border.bottom.color = "black",
              table.border.top.color = "white",
              heading.border.bottom.color = "black",
              table_body.hlines.color = "white",
              table.font.names = "Times New Roman")

print(table1_formatted)

```

```{r save-t1}
#save table
#save as word doc
#gtsave(table1_formatted, filename = "table1_word.docx", device = "word", path = here("outputs", "tables"), landscape = TRUE) #landscape doesn't work

#save as pdf
#gtsave(table1_formatted, filename = "table1.pdf") 

#save as html with larger column widths
table1_html <- table1_formatted %>% 
  cols_width(review_author_year ~ px(175), review_databases_searched ~ px(700), search_date_format ~ px(150), starts_with("n") ~ px(75))

#gtsave(table1_html, filename = "table_1.html", path = here("outputs", "tables"))

#export as excel to transfer to word - word output not working on gt table
#rio::export(t1, here("outputs", "tables", "t1_excel.xlsx"))

```


### Table 2. AMSTAR-2 Ratings per Question

```{r t2-amstar}
#re-format ratings to report in table 2
t2 <- amstar_rating_td %>% 
  mutate(review_author_year = as.factor(review_author_year)) %>% 
  mutate_if(is.character, ~case_when(. == "HIGH" ~ "H",
                                     . == "MODERATE" ~ "M",
                                     . == "LOW" ~ "L",
                                     . == "CRITICALLY LOW" ~ "CL",
                                     . == "Yes" ~ "Y",
                                     . == "Partial Yes" ~ "PY",
                                     . == "No" ~ "N",
                                     TRUE ~ .)) %>% 
  select(-refid, -amstar_11nrsi_rating, -amstar_9nrsi_rating) %>% #temporarily remove nrsi ratings to fit template
  arrange(str_to_lower(review_author_year))

#create gt table and format
t2_formatted <- t2 %>% 
  gt() %>% 
  cols_label(review_author_year = "Review", 
            amstar_overall_rating = "Overall",
            amstar_1_rating = "1",
            amstar_2_rating = "2",
            amstar_3_rating = "3",
            amstar_4_rating = "4",
            amstar_5_rating = "5",
            amstar_6_rating = "6",
            amstar_7_rating = "7",
            amstar_8_rating = "8",
            amstar_9rct_rating = "9",
            amstar_10_rating = "10",
            amstar_11rct_rating = "11",
            amstar_12_rating = "12",
            amstar_13_rating = "13",
            amstar_14_rating = "14",
            amstar_15_rating = "15",
            amstar_16_rating = "16") %>% 
  tab_style(style = list(cell_borders(sides = "all", color = "black", weight = px(1))),
            locations = cells_body(columns = everything())) %>% 
  tab_style(style = list(cell_borders(sides = "all", color = "black", weight = px(1)),
                         cell_text(weight = "bold")),
            locations = cells_column_labels()) %>% 
   tab_options(column_labels.border.top.color = "black",
              column_labels.border.bottom.color = "black",
              table_body.border.bottom.color = "black",
              table.border.top.color = "white",
              heading.border.bottom.color = "black",
              table_body.hlines.color = "white",
              table.border.bottom.color = "white",
              table.font.names = "Times New Roman") %>% 
  cols_width(review_author_year ~ px(175),
             amstar_overall_rating ~ px(75),
             everything() ~ px(35)) %>% 
  tab_style(style = cell_text(align = "center"), locations = cells_column_labels(columns = everything())) %>% 
  tab_style(style = cell_text(align = "left"), locations = cells_column_labels(columns = "review_author_year")) %>% 
  tab_style(style = cell_text(align = "center"), locations = cells_body(columns = everything())) %>% 
  tab_style(style = cell_text(align = "left"), locations = cells_body(columns = "review_author_year")) %>% 
  tab_footnote(footnote = "N = No; PY = Partial Yes; Y = Yes; CL = Critically Low; L = Low; M = Moderate; H = High") %>% 
  data_color(columns = 2:18,
             colors = scales::col_factor(palette = c("#ab1d1a", "#8ace7e", "#e03531", "#ffda66", "#e03531", "#b2dfa8", "#8ace7e"),
                                         domain = c("CL", "H", "L", "M", "N", "PY", "Y")))
             
          
print(t2_formatted)
```

```{r t2-save}
#save as HTML
#gtsave(t2_formatted, filename = "table_2.html", path = here("outputs", "tables"))

#save as word doc
#gtsave(t2_formatted, filename = "table2_word.docx", path = here("outputs", "tables"))

#export as excel to transfer to word - word output not working on gt table
#rio::export(t2, here("outputs", "tables", "t2_excel.xlsx"))
```

### Table 3. Risk of Bias in Included Systematic Reviews (ROBIS)

```{r t3-robis}
#remove leading numbers, select variables
t3 <- robis_rating_td %>% 
    mutate_if(is.character, ~case_when(. == "HIGH" ~ "High",
                                     . == "LOW" ~ "Low",
                                     . == "UNCLEAR" ~ "Unclear",
                                     TRUE ~ .)) %>% 
  select(review_author_year, ends_with("decision"), robis_overall_a, robis_overall_b, robis_overall_c, robis_overall_rating) %>% 
  arrange(str_to_lower(review_author_year))

#create gt table
t3_formatted <- t3 %>% 
  gt() %>% 
  cols_label(review_author_year = "Review", 
             robis_1_decision = "Domain 1",
             robis_2_decision = "Domain 2",
             robis_3_decision = "Domain 3",
             robis_4_decision = "Domain 4",
             robis_overall_a = "Interpretation",
             robis_overall_b = "Relevance",
             robis_overall_c = "Spin",
             robis_overall_rating = "Overall") %>% 
  tab_style(style = list(cell_borders(sides = "all", color = "black", weight = px(1))),
            locations = cells_body(columns = everything())) %>% 
  tab_style(style = list(cell_borders(sides = "all", color = "black", weight = px(1)),
                         cell_text(weight = "bold")),
            locations = cells_column_labels()) %>% 
   tab_options(column_labels.border.top.color = "black",
              column_labels.border.bottom.color = "black",
              table_body.border.bottom.color = "black",
              table.border.top.color = "white",
              heading.border.bottom.color = "black",
              table_body.hlines.color = "white",
              table.border.bottom.color = "white",
              table.font.names = "Times New Roman") %>% 
   cols_width(review_author_year ~ px(165),
              robis_overall_a ~ px(110),
              robis_overall_b ~ px(100),
              robis_overall_c ~ px(100),
              everything() ~ px(100),
              robis_overall_rating ~ px(50)) %>% 
  data_color(columns = 2:9,
             colors = scales::col_factor(palette = c("#e03531", "#8ace7e", "#e03531", "gray60", "#ef9997", "#b2dfa8", "#ffda66", "#8ace7e"),
                                         domain = c("High", "Low", "No", "No Information", "Probably No", "Probably Yes", "Unclear", "Yes")))


print(t3_formatted)

```

```{r t3-save}
#save as html
#gtsave(t3_formatted, filename = "table_3.html", path = here("outputs", "tables"))

#save as word doc
#gtsave(t3_formatted, filename = "table3_word.docx", path = here("outputs", "tables"))

#export as excel to transfer to word - word output not working on gt table
#rio::export(t3, here("outputs", "tables", "t3_excel.xlsx"))

```


### Appendices

#### Appendix 1. List of excluded reviews

```{r a1-excludedreviews}
#import citation info 
review_elig_citations <- spo_eligibility

#create df of excluded reviews and citations
a1_info <- review_elig_citations %>% 
  filter(eligibility_decision == "Not Eligible") %>% 
  filter(eligibility_exclude_reason != "Unclear") %>% 
  rename(citation = bibliography) %>% 
  select(citation, eligibility_exclude_reason) %>% 
  arrange(str_to_lower(stringi::stri_trans_general(citation, "Latin-ASCII")))

# temp <- a1_info %>% 
#   slice(1:50)
# 
# rio::export(temp, "refs_to_fix.xlsx")

# #create table
# a1_formatted <- a1_info %>% 
#   gt()  %>% 
#   cols_label(citation = "Excluded Review", 
#              eligibility_exclude_reason = "Reason for Exclusion") %>% 
#   tab_style(style = list(cell_borders(sides = "all", color = "black", weight = px(1))),
#             locations = cells_body(columns = everything())) %>% 
#   tab_style(style = list(cell_borders(sides = "all", color = "black", weight = px(1)),
#                          cell_text(weight = "bold")),
#             locations = cells_column_labels()) %>% 
#   tab_options(column_labels.border.top.color = "black",
#               column_labels.border.bottom.color = "black",
#               table_body.border.bottom.color = "black",
#               table.border.top.color = "white",
#               heading.border.bottom.color = "black",
#               table_body.hlines.color = "white",
#               table.border.bottom.color = "white",
#               table.font.names = "Times New Roman") %>% 
#   tab_header(title = md("**<div style='text-align: center;'>Appendix 1</div>**<div style='text-align: center; margin-top:10px; margin-bottom:20px;'>**List of Reviews Excluded at Full-Text Eligibility Assessment**<br></div>")) %>% 
#   tab_style(style = list(cell_text(align = "center")),
#             locations = cells_title(groups = "title")) %>% 
#     cols_align(
#     align = "left",
#     columns = everything()
#   ) 

a1_formatted <- a1_info %>% 
  gt() %>% 
  cols_label(
    citation = "Excluded Review", 
    eligibility_exclude_reason = "Reason for Exclusion"
  ) %>% 
  tab_style(
    style = list(
      cell_borders(sides = "all", color = "black", weight = px(1))
    ),
    locations = cells_body(columns = everything())
  ) %>% 
  tab_style(
    style = list(
      cell_borders(sides = "all", color = "black", weight = px(1)),
      cell_text(weight = "bold")
    ),
    locations = cells_column_labels()
  ) %>% 
  tab_style(
    style = cell_text(align = "left"),
    locations = cells_column_labels(columns = citation)
  ) %>% 
  tab_style(
    style = cell_text(align = "left"),
    locations = cells_body(columns = citation)
  ) %>% 
  tab_options(
    column_labels.border.top.color = "black",
    column_labels.border.bottom.color = "black",
    table_body.border.bottom.color = "black",
    table.border.top.color = "white",
    heading.border.bottom.color = "black",
    table_body.hlines.color = "white",
    table.border.bottom.color = "white",
    table.font.names = "Times New Roman"
  ) %>% 
  tab_header(
    title = md("**<div style='text-align: center;'>Appendix 1</div>**<div style='text-align: center; margin-top:10px; margin-bottom:20px;'>**List of Reviews Excluded at Full-Text Eligibility Assessment**<br></div>")
  ) %>% 
  tab_style(
    style = list(cell_text(align = "center")),
    locations = cells_title(groups = "title")
  )

print(a1_formatted)

```

```{r a1-save}
# #save as word
# gtsave(a1_formatted, filename = "appendix1_word.docx", path = here("outputs", "appendices"))
# 
# #save as html
# gtsave(a1_formatted, filename = "appendix_1.html", path = here("outputs", "appendices"))

#save as pdf
#gtsave(a1_formatted, filename = "appendix1_pdf.pdf")

#export as excel to transfer to word - word output not working on gt table
#rio::export(a1_info, here("outputs", "appendices", "a1_excel.xlsx"))
```


#### Appendix 2. Reviews awaiting classification 

```{r a3-awaitingclassification}
#create df with studies awaiting classification
a3_info <- review_elig_citations %>% 
  filter(eligibility_exclude_reason == "Unclear") %>% 
  mutate(eligibility_notes = str_remove_all(eligibility_notes, "\\(.*?\\)")) %>% 
  mutate(eligibility_notes = str_remove_all(eligibility_notes, "; Review")) %>% 
  rename(citation = bibliography) %>% 
  select(citation, eligibility_notes) %>% 
  arrange(str_to_lower(stringi::stri_trans_general(citation, "Latin-ASCII")))



#create formatted gt table
a3_formatted <- a3_info %>% 
  gt()  %>% 
  cols_label(citation = "Review", 
             eligibility_notes = "Reason") %>% 
  tab_style(style = list(cell_borders(sides = "all", color = "black", weight = px(1))),
            locations = cells_body(columns = everything())) %>% 
  tab_style(style = list(cell_borders(sides = "all", color = "black", weight = px(1)),
                         cell_text(weight = "bold")),
            locations = cells_column_labels()) %>% 
  tab_options(column_labels.border.top.color = "black",
              column_labels.border.bottom.color = "black",
              table_body.border.bottom.color = "black",
              table.border.top.color = "white",
              heading.border.bottom.color = "black",
              table_body.hlines.color = "white",
              table.border.bottom.color = "white",
              table.font.names = "Times New Roman") %>% 
  tab_header(title = md("**<div style='text-align: center;'>Appendix 2</div>**<div style='text-align: center; margin-top:10px; margin-bottom:20px;'>**List of Reviews Awaiting Classification**<br></div>")) %>% 
  tab_style(style = list(cell_text(align = "center")),
            locations = cells_title(groups = "title"))

print(a3_formatted)


```

```{r a3-save}
# # #save as word
# gtsave(a3_formatted, filename = "appendix2_word.docx", path = here("outputs", "appendices"))
# 
# #save as html
# gtsave(a3_formatted, filename = "appendix_2.html", path = here("outputs", "appendices"))

# #save as pdf
# gtsave(a3_formatted, filename = "appendix3_pdf.pdf")

#export as excel to transfer to word - word output not working on gt table
#rio::export(a3_info, here("outputs", "appendices", "a3_excel.xlsx"))
```

#### Appendix 3. Descriptive characteristics for each included systematic review

```{r a4-reviewchar}
# Create COI variable and Critical Appraisal section
spo_review_info <- spo_review_level %>%
  mutate(
    review_coi = case_when(
      amstar_16_rating == "No" ~ "Lacks reporting on funding and/or conflicts of interest",
      
      !is.na(amstar_16_coi_the_authors_reported_no_competing_interests_or) &
      is.na(amstar_16_coi_the_authors_described_their_funding_sources_and_how_they_managed_potential_conflicts_of_interest) ~
        "The authors declared no competing interests",
      
      is.na(amstar_16_coi_the_authors_reported_no_competing_interests_or) &
      !is.na(amstar_16_coi_the_authors_described_their_funding_sources_and_how_they_managed_potential_conflicts_of_interest) ~
        "Disclosed funding sources and management of any potential conflicts of interest",
      
      !is.na(amstar_16_coi_the_authors_reported_no_competing_interests_or) &
      !is.na(amstar_16_coi_the_authors_described_their_funding_sources_and_how_they_managed_potential_conflicts_of_interest) ~
        "The authors declared no competing interests and/or disclosed funding sources and management of any potential conflicts",
      
      TRUE ~ NA_character_
    ),
    review_critical_appraisal = paste0(
  "AMSTAR-2: ", 
  str_to_sentence(ifelse(is.na(amstar_overall_rating), "Not reported", amstar_overall_rating)),
  " <br> ROBIS: ", 
  str_to_sentence(ifelse(is.na(robis_overall_rating), "Not reported", robis_overall_rating))
)
  ) %>%
  select(refid, review_coi, review_critical_appraisal)

#select relevant appendix 4 info
a4_info <- review_td %>%
  #left_join(numelig_perreview) %>%
  left_join(numinc_perreview) %>%
  left_join(spo_review_info, by = "refid") %>%
  mutate(search_date_format = ifelse(nchar(review_search_date) == 10, format(ymd(review_search_date), "%B %d, %Y"), review_search_date)) %>%
  mutate(search_date_format = ifelse(nchar(review_search_date) == 7, format(ym(review_search_date), "%B %Y"), search_date_format)) %>%
  mutate(across(everything(), ~ifelse(.x == -999, "Not reported", .x)),
         n_included = as.character(n_included)#,
         #n_eligible = as.character(n_eligible)
         ) %>%
  select(refid, review_author_year, starts_with("review_eligibility"), review_databases_searched,
         search_date_format, n_included, review_flow_diagram, review_registration_number, review_availability_statement, 
         review_coi, review_critical_appraisal) %>% # n_eligible,
  arrange(str_to_lower(review_author_year))

#create df of review_author_year and refid for merging
review_idbyname <- review_td %>%
  select(refid, review_author_year)

#select citation info for eligible reviews
review_citations <- review_elig_citations %>%
  janitor::clean_names() %>%
  left_join(review_idbyname) %>%
  filter(!is.na(review_author_year)) %>%
  rename(citation = bibliography) %>% 
  select(refid, citation, title)

#import linked citations for all references
linked_ref_df <- import(here("data", "SPO_linked_references.csv")) %>%
  janitor::clean_names()

#pull list of included refids
inc_rev <- review_citations$refid

#transform for merging
linked_ref_td <- linked_ref_df %>%
  filter(refid %in% inc_rev) %>%
  select(refid, linked_refid) %>%
  left_join(review_citations) %>%
  left_join(review_elig_citations, by = c("linked_refid" = "refid")) %>%
  rename(main_citation = citation,
         linked_citation = bibliography) %>%
  select(refid, main_citation, starts_with("linked")) %>%
  pivot_longer(cols = c(main_citation, linked_citation),
               names_to = "citation_type",
               values_to = "citation",
               values_drop_na = TRUE) %>%
  mutate(citation_refid = case_when(citation_type == "main_citation" ~ as.character(refid),
                                    citation_type == "linked_citation" ~ as.character(linked_refid))) %>%
  select(-c(linked_refid, citation_type, linked_references)) %>%
  filter(refid != citation_refid)

#create variable that combines all references for a review into one cell
review_reports <- review_citations %>%
  select(refid, citation) %>%
  mutate(citation_refid = "") %>%
  rbind(linked_ref_td) %>%
  group_by(refid) %>%
  summarize(all_reports = paste(citation, collapse = " <br><br> ")) %>%
  mutate(all_reports = stringi::stri_trans_general(all_reports, "Latin-ASCII")) %>%
  ungroup()


#extract titles from citation df
rev_titles <- review_citations %>%
  select(refid, title)

#merge titles and citations with other a4 info and format eligibility cells
a4 <- a4_info %>%
  left_join(rev_titles, by = "refid") %>%
  left_join(review_reports, by = "refid") %>%
  select(review_author_year, title, review_eligibility_participant:review_availability_statement, review_coi,
         review_critical_appraisal, all_reports) %>%
#cosmetics for table
  mutate_at(vars(starts_with("review_eligibility"), review_availability_statement), list(~ str_replace_all(., "\\s+-\\s+(?=[A-Z])", "<br> - "))) %>%
  mutate_at(vars(starts_with("review_eligibility"), review_availability_statement), ~ str_replace_all(., "- +([\"'a-zA-Z])", " <li>\\1")) %>%
  mutate_at(vars(starts_with("review_eligibility")), ~ paste0("<ul>", ., "</ul>")) %>%
  mutate(review_availability_statement = ifelse(str_detect(review_availability_statement, "<li>"),
                                                paste0("<ul>", review_availability_statement, "</ul>"),
                                                review_availability_statement))

```


```{r a4-formatting}
#split data frame into list of data frames
a4_dflist <- map(1:nrow(a4), ~a4[.x, ])

#transfer to long format
df_list_long <- map(a4_dflist, ~ .x %>%
                      pivot_longer(cols = everything(),
                                   names_to = "variable",
                                   values_to = "value") %>%
                      mutate(variable = case_when(variable == "review_author_year" ~ "Review",
                                                  variable == "title" ~ "Title",
                                                  variable == "review_eligibility_participant" ~ "Participants",
                                                  variable == "review_eligibility_intervention" ~ "Interventions",
                                                  variable == "review_eligibility_comparator" ~ "Comparisons",
                                                  variable == "review_eligibility_outcome" ~ "Outcomes",
                                                  variable == "review_eligibility_timing" ~ "Timing",
                                                  variable == "review_eligibility_setting" ~ "Setting",
                                                  variable == "review_eligibility_design" ~ "Design",
                                                  variable == "review_databases_searched" ~ "Databases Searched",
                                                  variable == "search_date_format" ~ "Search Date",
                                                  variable == "review_flow_diagram" ~ "Prisma Diagram",
                                                  variable == "review_registration_number" ~ "Registration",
                                                  variable == "review_availability_statement" ~ "Data Availability Statement",
                                                  variable == "review_coi" ~ "Conflict of Interest",
                                                  variable == "review_critical_appraisal" ~ "Critical Appraisal",
                                                #  variable == "n_eligible" ~ "Eligible Studies",
                                                  variable == "n_included" ~ "Included Studies",
                                                  variable == "all_reports" ~ "References",
                                                  TRUE ~ variable)))

#combine into one single data frame
combined_a4 <- bind_rows(df_list_long, .id = "source") %>%
  mutate(source = as.numeric(source))

#create gt table for each for each review
list_gt <- lapply(split(combined_a4, combined_a4$source), function(x) {
  gt(x) %>%
    cols_hide("source") %>%
    cols_label(variable = "",
               value = "") %>%
    tab_style(style = list(cell_text(weight = "bold")),
            locations = cells_body(columns = "variable")) %>%
    tab_row_group(rows = 3:9, label = "Eligibility Criteria:") %>%
    tab_row_group(rows = 1:2, label = "", id = "group1") %>%
    tab_options(table.font.names = "Times New Roman",
                table.width = pct(100)) %>%
    tab_style(style = cell_text(weight = "bold"), locations = cells_row_groups()) %>%
    tab_style(style = cell_text(align = "right"), locations = cells_body(columns = "variable", rows = 3:9)) %>%
    fmt_markdown(columns = everything())
})

#add title
a4_title_html <- '<h2 style="text-align:center;font-family:Times New Roman;font-size:20px;margin-bottom:5px;margin-top:25px;">
  <div>Appendix 3</div>
  <div style="margin-top:10px; margin-bottom:10px;">Characteristics of Included Reviews</div>
</h2>'


#extract HTML code of table
html_code <- list_gt %>%
  map(as_raw_html) %>%
  reduce(paste) %>%
  paste(a4_title_html, ., sep = "\n")

#print in document
htmltools::browsable(htmltools::HTML(html_code))
```

```{r a4-save}
#save as HMTL
#writeLines(html_code, here("outputs", "appendices", "appendix_3.html"))

#test word output
#couldnt get to work - output to excel and import into word
#rio::export(combined_a4, here("outputs", "appendices", "a3_excel.xlsx"))

# combined_a4 <- combined_a4 %>%
#   mutate(source = paste("Review", source))

# # EXPORT WORD
# a4_word <- combined_a4 %>%
#   mutate(
#     value = value %>%
#       str_replace_all("<ul>", "") %>%
#       str_replace_all("</ul>", "") %>%
#       str_replace_all("<li>", "• ") %>%
#       str_replace_all("</li>", "\n")
#   ) %>%
#   gt(groupname_col = "source") %>%
#   cols_hide("source") %>%
#   cols_label(
#     variable = "",
#     value = ""
#   ) %>%
#   tab_style(
#     style = cell_text(weight = "bold"),
#     locations = cells_body(columns = "variable")
#   ) %>%
#   tab_options(
#     table.font.names = "Times New Roman",
#     table.width = pct(100)
#   )#%>%
#   #fmt_markdown(columns = everything())
# 
# gtsave(
#   a4_word,
#   filename = here::here("outputs", "appendices", "appendix_3.docx")
# )

```


```{r export-rds}
# #export appendices and tables for technical report (without titles)
# 
# #Combine all gt tables into a list
# tables_list <- list(table1 = table1_formatted,
#                     table2 = t2_formatted,
#                     table3 = t3_formatted,
#                     table4 = t4_formatted,
#                     appendix1 = a1_formatted %>% tab_header(title = NULL, subtitle = NULL),
#                     appendix2 = a2_formatted %>% tab_header(title = NULL, subtitle = NULL),
#                     appendix3 = a3_formatted %>% tab_header(title = NULL, subtitle = NULL),
#                     appendix4 = combined_a4,
#                     appendix5 = combined_a5)
# 
# #Save as RDS object to data directory
# saveRDS(tables_list, file = "data/tables_list.rds")
```



# Info for Translational Product

Information for initial translational product (to fill out comms team excel file)

```{r translational-results}
# #study locations
# count_country
# 
# #academic levels
# #number/% studies in elementary or primary school
# study_elem 
# study_elem_per 
# 
# sum(!is.na(study_td$study_school_level_elementary_school)) + 
# sum(!is.na(study_td$study_school_level_only_reported_primary_school))
# 
# #number/% studies in middle school
# study_mid 
# study_mid_per
# 
# #number/% studies in high or secondary school
# study_high 
# study_high_per 
# 
# sum(!is.na(study_td$study_school_level_high_school)) + 
# sum(!is.na(study_td$study_school_level_only_reported_secondary_school))
# 
# #included studies
# length(unique(study_td$refid))
# 
# #number of students
# num_studs
# 
# #median age and range
# min(study_td$study_age_average, na.rm = TRUE) 
# max(study_td$study_age_average, na.rm = TRUE)
# median(study_td$study_age_average, na.rm = TRUE)
# 
# #number of studies not reporting any race/ethnicity
# race_cols <- c("study_percent_aian", "study_percent_asian", "study_percent_black", "study_percent_nhpi",
#                "study_percent_white", "study_percent_hispanic", "study_percent_mixed", "study_percent_other")
# num_raceNR <- sum(rowSums(is.na(study_td[race_cols])) == length(race_cols))
# per_raceNR <- paste0(round(num_raceNR / length(unique(study_td$refid)) * 100, 2), "% of studies didn't report race/ethnicity")
# per_raceNR
# 
# #average (or median) and SD of % white students
# format_percent(median(study_td$study_percent_white, na.rm = TRUE) * 100, 2)
# format_percent(mean(study_td$study_percent_white, na.rm = TRUE) * 100, 2)
# format_percent(sd(study_td$study_percent_white, na.rm = TRUE) * 100, 2)
# #DIFFERENCE IN MEDIAN AND MEAN DRIVEN BY 100% OF CANADIAN STUDY SAYING "OTHER RACE"
# 
# #median number of students per study and range
# median(study_td$study_number_participants, na.rm = TRUE)
# min(study_td$study_number_participants, na.rm = TRUE)
# format_thousands(max(study_td$study_number_participants, na.rm= TRUE))
# 
# #total, and median/range of number of classrooms per study
# sum(study_td$study_number_classrooms, na.rm = TRUE)
# median(study_td$study_number_classrooms, na.rm = TRUE)
# min(study_td$study_number_classrooms, na.rm = TRUE)
# max(study_td$study_number_classrooms, na.rm = TRUE)
# 
# #total, and median/range of number of schools per study
# sum(study_td$study_number_schools, na.rm = TRUE)
# median(study_td$study_number_schools, na.rm = TRUE)
# min(study_td$study_number_schools, na.rm = TRUE)
# max(study_td$study_number_schools, na.rm = TRUE)
# 
# #number and percentage of facilitators/providers
# count_intprovider 
# 
# #number of students per MA outcome
# ## Anxiety Diagnoses
# ad_ma_df <- import(here("data", "Anxiety_diagnosis.xlsx"))
# ad_refid <- unique(ad_ma_df$refid) #8
# ad_num_stud <- study_td %>% 
#   filter(refid %in% ad_refid) %>% 
#   summarize(n_stud = sum(study_number_participants)) %>% 
#   pull(n_stud)
# ad_num_stud
# 
# ## Anxiety Symptoms
# as_ma_df <- import(here("data", "Anxiety_Symptoms.xlsx"))
# as_refid <- unique(as_ma_df$refid) #32
# as_num_stud <- study_td %>% 
#   filter(refid %in% as_refid) %>% 
#   filter(refid != 10062) %>% #removed from analysis - MSC
#   summarize(n_stud = sum(study_number_participants)) %>% 
#   pull(n_stud)
# as_num_stud
# 
# ## Depression Symptoms
# ds_ma_df <- import(here("data", "Depression_Symptoms.xlsx"))
# ds_refid <- unique(ds_ma_df$refid) #18
# ds_num_stud <- study_td %>% 
#   filter(refid %in% ds_refid) %>% 
#   filter(refid != 10062) %>%  #removed from analysis - MSC
#   summarize(n_stud = sum(study_number_participants)) %>% 
#   pull(n_stud)
# ds_num_stud

```



## END